---
title: "Noontime Crimes"
output:
  html_document: default
  html_notebook: default
---

```{r global_options, include = F}
knitr::opts_chunk$set(fig.width = 10, fig.height = 6,
                      warning = F, message = F, fig.path = 'figs/')
```

```{r load_data_setup, message = F}
library(tidyverse)
library(scales)
library(DT)
library(forcats)
library(ggthemes)

crimes <- read_rds('../processed_data/crimes.rds')
```

# Overall Crimes by Time of Day
```{r overal_time_of_day}
crimes_by_day <- crimes %>%
  group_by(year, hour_of_day) %>%
  summarize(crime_count = n() / length(unique(date_occ)))
crimes_by_day %>%
  ggplot(aes(hour_of_day, crime_count)) + 
  geom_line() + 
  facet_grid(~ year ) + 
  scale_y_continuous(limits = c(0, 75)) +
  scale_x_continuous(breaks = c(0,12,23)) +
  ggtitle('Crime Rates Would Appear to Peak around Noon') + 
  ylab('Average Amount of Crimes per Day') + 
  xlab('Hour of day: 12:00AM (0) - 11PM (23)') + 
  theme_bw()
```

## What Crime Contribute to this Peak in Noon Crimes?
Let's take a closer look and split by different types of crimes. To start, we'll break down all `r length(unique(crimes$crm_desc))` unique crime types with the following "crime buckets" (subjectively binned by Patrick and myself)

```{r which_crimes}
crimes_by_day <- crimes %>%
  filter(!grepl('MISS', simple_bucket)) %>%
  group_by(simple_bucket, hour_of_day) %>% 
  summarize(crime_count = n() / length(unique(date_occ))) %>%
  ungroup() %>%
  mutate(simple_bucket = fct_reorder(simple_bucket, crime_count))
crimes_by_day %>%
  ggplot(aes(hour_of_day, crime_count, color = simple_bucket)) + 
  geom_line() + 
  facet_grid(simple_bucket ~ ., scales = 'free') +
  ggtitle("FRAUD, SEXUAL, THEFT, and 'OTHER' Crimes Show Pronounced Peaks at Noon") + 
  xlab('Hour of day: 12:00AM (0) - 11PM (23)') + 
  ylab('Average Amount of Crimes per Day') +
  theme_bw()
```

## Investigate these Crimes Further
```{r}
high_noon_crimes <- c("FRAUD","SEXUAL","THEFT","OTHER")
day_of_week_check <- crimes %>%
  filter(simple_bucket %in% high_noon_crimes) %>%
  group_by(simple_bucket, day_of_week, hour_of_day) %>%
  summarize(crime_count = n() / length(unique(date_occ))) %>%
  ungroup() %>%
  mutate(day_of_week = fct_relevel(day_of_week,
    c('Sunday', 'Monday', 'Tuesday', 'Wednesday', 'Thursday',
    'Friday', 'Saturday')
  ))
day_of_week_check %>%
  ggplot(aes(hour_of_day, crime_count, color = simple_bucket)) + 
  geom_line() + 
  facet_grid(day_of_week ~ simple_bucket, scales = 'free') + 
  theme_bw() + 
  scale_y_continuous(limits = c(0, 35), breaks = c(10, 30)) +
  ggtitle("Theft-Type Crimes Contribute the Most to Noon Peak",
          subtitle = 'Noon is Probably Default time of Crime when Time of Crime Ocurring is Unknown') + 
  xlab('Hour of day: 12:00AM (0) - 11PM (23)') + 
  ylab('Average Amount of Crimes per Day')
```

## Is Theft Centered at only one Area?
```{r theft_in_areas}
theft_areas <- crimes %>%
  filter(simple_bucket == 'THEFT') %>%
  group_by(area_name, hour_of_day) %>%
  summarize(crime_count = n() / length(unique(date_occ)))
theft_areas %>%
  ggplot(aes(hour_of_day, crime_count, color = area_name)) +
  geom_line() + 
  theme_bw() + 
  scale_y_continuous(limits = c(0, 2.5)) +
  facet_wrap(~ area_name) + 
  theme(legend.position = 'none') + 
  ggtitle('Default Noon Placeholder Appears to be Widespread') + 
  xlab('Hour of day: 12:00AM (0) - 11PM (23)') + 
  ylab('Average Amount of Crimes per Day')
```

## Why is This Important?